\Large UC President's Postdoctoral Fellowship Research Statement: \\ \textbf{How Unique is the Solar System? Planetary Luminosities as Fingerprints for the Origins and Properties of Exoplanets}

### 2016-11-05 Postdoc Applications/AnaMariaPisoResume.tex
upd

Harvard-Smithsonian Center for Astrophysics & {\it Phone:}    (617) 818-6780 \\         
60 Garden Street, MS-10 & {\it E-mail:}  apiso@cfa.harvard.edu\\       
Cambridge, MA  02138  & {\it WWW:} www.cfa.harvard.edu/$\sim$apiso \\     
\end{tabular}

@@

\section{\sc Education}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] Ph.D., Astronomy \& Astrophysics, May 2016
\item[] Advisor: Prof. Karin \"Oberg 
\item[] Thesis Title: ``Origins of Gas Giant Compositions: The Role of Disk Location and Dynamics''   
\end{list1}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] A.M., Astronomy \& Astrophysics, May 2013
\item[] Advisor: Dr. Ruth Murray-Clay
\item[] Research Exam Project: ``On the Minimum Core Mass for Giant Planet Formation''
\end{list1}
{\bf Massachusetts Institute of Technology}, Cambridge, MA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] S.B., Physics,  June 2010 \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, Major GPA: 4.6/5.0
\item[] S.B., Mathematics, June 2010\,\,\,\, Major GPA: 4.8/5.0
\end{list1}

@@

\item[] {\bf Postdoctoral Fellow} \hfill {\bf September 2016 - }
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] UCLA, Earth, Planetary and Space Sciences Department \hfill \textit{Los Angeles, CA}
%\item[] Project: The Magnetic Field Signature of Super Earths
\item[] Advisor: Prof. Hilke Schlichting \\
\end{list1}

@@

\item[] {\bf Assistant manager} \hfill {\bf November 2005 - June 2006}
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] Neuron Group S.R.L. Software Company \hfill \textit{Bucharest, Romania}
\item[] Digital map designer and database manager for the '112 Emergency Call Center' national project
%\item[] Advisors: Dr. Paola Rebusco \& Prof. Edmund Bertschinger
\end{list1}
\end{list2}

@@

\item[] {\bf WISTEM Program Mentor} \hfill {\bf September 2013 - present}
\begin{list1}
\item[] Mentor for a Harvard College undergraduate \hfill \textit{Cambridge, MA}
\end{list1}

@@

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, Pegues, J., \& \"Oberg, K.I. \textit{The Role of Ice Compositions and Morphology For Snowlines and the C/N/O Ratios in Active Disks}. ApJ, submitted \\
\end{list2}

@@

@@

>>>>

Department of Earth, Planetary, and Space Sciences & {\it Phone:}    (617) 818-6780 \\         
595 Charles E. Young Dr. East & {\it E-mail:}  apiso@ucla.edu\\       
Los Angeles, CA 90095  & {\it WWW:} www.cfa.harvard.edu/$\sim$apiso \\     
\end{tabular}

@@

\section{\sc Education}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] Ph.D., Astronomy \& Astrophysics, April 2016
\item[] Advisor: Prof. Karin \"Oberg 
\item[] Thesis Title: ``Origins of Gas Giant Compositions: The Role of Disk Location and Dynamics''   
\end{list1}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] A.M., Astronomy \& Astrophysics, May 2013
\item[] Advisor: Dr. Ruth Murray-Clay
\item[] Research Exam Project: ``On the Minimum Core Mass for Giant Planet Formation''
\end{list1}
{\bf Massachusetts Institute of Technology}, Cambridge, MA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] S.B., Physics,  June 2010 % \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, Major GPA: 4.6/5.0
\item[] S.B., Mathematics, June 2010% \,\,\,\, Major GPA: 4.8/5.0
\end{list1}

@@

\item[] {\bf Postdoctoral Scholar} \hfill {\bf September 2016 - present}
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] UCLA, Department of Earth, Planetary, and Space Sciences \hfill \textit{Los Angeles, CA}
%\item[] Project: The Magnetic Field Signature of Super Earths
\item[] Advisor: Prof. Hilke Schlichting \\
\end{list1}

@@

\item[] {\bf Assistant manager} \hfill {\bf November 2005 - June 2006}
%{\bf Harvard-Smithsonian Center for Astrophysics} \hfill \textit{Cambridge, MA}
\begin{list1}
%\vspace{-0.1in}
\item[] Neuron Group S.R.L. Software Company \hfill \textit{Bucharest, Romania}
\item[] Digital map designer and database manager for the '112 Emergency Call Center' project
%\item[] Advisors: Dr. Paola Rebusco \& Prof. Edmund Bertschinger
\end{list1}
\end{list2}

@@

\item[] {\bf WISTEM Program Mentor} \hfill {\bf September 2013 - May 2016}
\begin{list1}
\item[] Mentor for a Harvard College undergraduate \hfill \textit{Cambridge, MA}
\end{list1}

@@

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, Pegues, J., \& \"Oberg, K.I. \textit{The Role of Ice Compositions and Morphology For Snowlines and the C/N/O Ratios in Active Disks}. ApJ, accepted: arXiv:1611.00741  \\
\end{list2}

@@

\begin{list2}
\item[] {\bf Origins of Gas Giant Compositions: The Role of Disk Location and Dynamics} \\
iPLEX Lunch Seminar, Los Angeles, CA, September 2016\\
Invited talk \\
\end{list2}

@@

\begin{list2}
\item[] {\bf Giant Planet Formation and Snowlines in Protoplanetary Disks} \\
CfA Small Scale Seminar, Cambridge, MA, February 2016\\
Invited talk \\
\end{list2}
